### 2019-08-21 maciek.tex

In this section we assume the Online Clustering problem with the existence of a perfect partition of the input graph.

\begin{theorem}
  The competitive ratio of any deterministic algorithm for Online Clustering (with perfect partition) is $\Omega(k\cdot \ell)$.
\end{theorem}

@@

  \begin{enumerate}
    \item Clusters A and B with components of size k-1. Define x and y.
    \item The input sequence (after these glueing) is to keep asking for x and someone of x's color
    \item Define a sequence of xs and ys for any deterministic algorithm.
    \item Define what OPT should do: the cluster D and nodes d1 d2 that should be hidden from the sequence of xs (and ys?)
    \item (somewhere) define c(x): it is easy when x is not from D: then any would do; if x is from D, then issue request between non-d1/d2
    \item Argue that OPT does not pay for input sequence (after glueing)
    \item bound the number of times we can issue (x, c(x)) request
  \end{enumerate}
\end{proof}

@@

\begin{theorem}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest feasible partition}
  \label{rebalancing-cost}
\end{theorem}

>>>>

In this section we assume the Online Balanced Partition problem with the existence of a perfect partition of the input graph.

\begin{theorem}
  The competitive ratio of any deterministic algorithm for Online Balanced Partition (with perfect partition) is $\Omega(k\cdot \ell)$.
\end{theorem}

@@

  \begin{enumerate}
    \item Clusters A and B with components of size k-1. Define x and y.
    \item The input sequence (after these glueing) is to keep asking for x and someone of x's color
    \item Define a sequence of xs and ys for any deterministic algorithm.
    \item Define what OPT should do: the cluster D and nodes d1 d2 that should be hidden from the sequence of xs (and ys?)
    \item (somewhere) define c(x): it is easy when x is not from D: then any would do; if x is from D, then issue request between non-d1/d2
    \item Argue that OPT does not pay for input sequence (after glueing)
    \item lower-bound the number of times we can issue (x, c(x)) request
  \end{enumerate}
\end{proof}

@@

\begin{theorem}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{theorem}
